%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Alex Giovannelli} \\ \vspace{5pt}
    \small \faPhone* \texttt{740.258.9709} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{agiovannelli2234@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Blacksburg, VA}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {Virginia Polytechnic Institute and State University}{Aug. 2021 -- Present}
      {Graduate Teaching Assistant}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Advisal of students during scheduled office hours and class lectures}
        \resumeItem{In-class assistant for course instructor}
        \resumeItem{Maintain honor code in accordance to university policy via code review process}
      \resumeItemListEnd

    \resumeSubheading
      {JPMorgan Chase \& Co.}{Jul. 2018 -- Jul. 2021}
      {Associate Software Engineer}{Columbus, OH}
      \resumeItemListStart
        \resumeItem{Design and development of front-end features for Chase.com (i.e. Chase Offers, Security Center, Chase Relief Hub, Saved Account Manager, etc.)}
        \resumeItem{Generation of technical documentation for product owners and programmers}
        \resumeItem{Subject-matter expert in automation testing and CI/CD initiatives}
        \resumeItem{Mentorship of new employees and interns}
        \resumeItem{\textbf{Highlights}: Promoted from Software Engineering Program after one year of service, lead developer for COVID-19 Support hub, lead volunteer in Software Engineering Program recruitment workstream}
      \resumeItemListEnd

    \resumeSubheading
      {Siemens Healthineers}{Jan. 2017 -- Aug. 2017}
      {Software Engineering Intern}{Forchheim, DE}
      \resumeItemListStart
        \resumeItem{Development of software in advanced therapy devices}
        \resumeItem{Creation and documentation of high-level structures of the system design}
        \resumeItem{Representative in international software system integration meetings}
        \resumeItem{Scrum Master for two development iterations}

    \resumeItemListEnd
    
    \resumeSubheading
      {Granville Exempted Village Schools}{May 2016 -- Jul. 2016}
      {Systems Administrator Intern}{Granville, OH}
      \resumeItemListStart
        \resumeItem{Provision of systems administration support for Windows and Linux systems including server and workstation upgrades}
        \resumeItem{Development and deployment of operating system applications, packages, and images}
        \resumeItem{Management of summer technician team operations}
        
    \resumeItemListEnd
    
    \resumeSubheading
      {Matrix Technologies, Inc.}{Aug. 2015 -- Dec. 2015}
      {Computer Programmer and Systems Analyst Intern}{Maumee, OH}
      \resumeItemListStart
        \resumeItem{Generation of new software and modifications in accordance to Agile methodology}
        \resumeItem{Management of internally-developed software for Project Managers}
        \resumeItem{Maintenance of database for storage of project data}
        \resumeItem{Manual creation for use of internal software tools}
        \resumeItem{Process Improvement Team member; \textbf{received a return offer} for a full-time position}
        
  \resumeItemListEnd

    \resumeSubheading
      {Matrix Technologies, Inc.}{Aug. 2014 -- Dec. 2014}
      {Computer Programmer and Systems Analyst Intern}{Maumee, OH}
      \resumeItemListStart
        \resumeItem{Enhancement and expansion of internal software solutions}
        \resumeItem{Coordination of project design changes with stakeholders}
        \resumeItem{Research for unit test implementations in existing software}
        \resumeItem{Process Improvement Team member; \textbf{received a return offer} for an internship position}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Virginia Polytechnic Institute and State University}{Aug. 2021 -- May 2023}
      {Master's of Science in Computer Science}{Blacksburg, VA}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Information Retrieval, Programming Languages}
        \resumeItemListEnd
        
    \resumeSubheading
      {University of Cincinnati}{Aug. 2013 -- May 2018}
      {Bachelor's of Science in Computer Engineering}{Cincinnati, OH}
      	\resumeItemListStart
    	\resumeItem {\textbf{Achievements}: Admitted in honors International Cooperative Education Program for German Experience, Cincinnatus scholarship recipient}
        \resumeItem {\textbf{Minors}: Computer Science, German Studies}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section {PROJECTS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {3DUI Virtual Reality Technique Enhancement}{Oct. 2021 -- Present}
      {Research Project}{}
      	\resumeItemListStart
      	% Project summary
      	\resumeItem{\textbf{Summary}: Research and improve upon several classic 3DUI interaction techniques in virtual reality}
      	\resumeItem {\textbf{Discipline}: Human-Computer Interaction}
    	\resumeItem {\textbf{Technologies}: C\#, Unity, SteamVR}
        \resumeItemListEnd
    \resumeSubheading
      {Empirical Evaluation of Web Applications using JavaScript and WebAssembly}{Aug. 2021 -- Dec. 2021}
      {Course Project}{}
      	\resumeItemListStart
      	% Project summary
      	\resumeItem{\textbf{Summary}: Creation of WebAssembly and JavaScript workbench for evaluation of programming language execution time and energy efficiency}
      	\resumeItem {\textbf{Discipline}: Software Engineering}
    	\resumeItem {\textbf{Technologies}: Go, JavaScript, Rust, HTML/CSS, Git}
        \resumeItemListEnd
        
    \resumeSubheading
      {Empirical Study of Neural Question-Answering Models}{Aug. 2021 -- Dec. 2021}
      {Course Project}{}
      	\resumeItemListStart
    	\resumeItem {\textbf{Summary}: Generation of Jupyter Notebooks to test and compare deep neural models against question-answering task}
    	\resumeItem {\textbf{Discipline}: Machine Learning}
    	\resumeItem {\textbf{Technologies}: Python, Jupyter Notebook, Git}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming Languages} {: JavaScript, Python, Go, Java, C\#, HTML/CSS}\vspace{2pt} \\
     \textbf{Tools}     {: Unity, Git, Jira, Figma, Cucumber, axe DevTools, Azure DevOps Server, SteamVR}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
